%An in-depth explanation of the problem, including the "business case". What is wrong with the status-quo or what opportunity exists that justifies undertaking this project (expanding upon the problem statement)? If you have a clear customer or sponsor, why do they want you to work on this? What is the existing relationship, if any, between the development team and the customer? This section should occupy 1/2 - 1 full page.

The current problem with inventory system in place now is that it takes tremendous effort by our customer to keep track of all items in the system. The current system consists of an excel spreadsheet that is used to track each individual asset in the nursing department's inventory which amounts to more than 150 assets (not including non-assets) located in two different buildings on UTA's campus. Requests for use of inventory items are handled using physical forms which document the purpose and time on which an asset is checked out for use. Items checked out for an extended period of time would require a constant reminder that they are still in use by, in our customer's case, hanging the document on a board. Accessing and editing the excel spreadsheet is all conducted from the Simulation Inventory Specialist's computer. The excel sheet is solely managed by one person in the department, The Simulation Inventory Specialist, in which they are responsible for processing requests, repairs, and the retirement of the equipment on a day-to-day basis. 

Our customer requests the development of the SmartInventory application to help reduce the load of work on the individual specialist working on the current inventory system. There currently isn't a development team on hand working on this specific solution so this will be a fresh approach to develop this application. One of the aims of this assignment is to develop a relationship with our customer in order to deliver a solution that satisfies their needs and also provide a inventory application that minimizes the occurrence of human error. 