%Who are the stakeholders of the project? Who will be the point of contact from the sponsor or customer side? Who are the team members, and what will be their areas of responsibility? Will your team maintain the product owner and scrum master for the whole project, or will that role change periodically? This section should occupy 1/2 - 1 full page.
Aside from the team members of the SmartInventory App being shareholders, the Simulation Inventory Specialist for the Nursing Department, Jacquelyn Donaldson, is also a shareholder. Nguyen Le, Alexander Martinez, Kennedy Mosoti, and Bradley Norman compose of the team members, which is a combination of half software engineers and other half computer scientists.

Bradley Norman will be point of contact for our sponsor and customer, Jacquelyn Donaldson, using Outlook UTA email to communicate  and schedule meetings before and after sprints or whenever each party deems it necessary. The title scrum master will be change periodically to allow each member the opportunity to experience leadership.

Since the project will be divided in three areas: Front-end, Application Programming Interface (API), and Back-end. We will attempt to divide the work evenly as much as possible, by having Kennedy and Bradley work on the Front-end while simultaneously Alexander and Nguyen working on the Back-end. Then converging collaboratively on the API. The Front-end is what the SmartInventory Application which the users see's, all the different graphic user interface options. The API is how the Front-end and Back-end interact, sending or receiving data. The Back-end is where all the data is stored for the assets and non-assets. As a whole, we all have a responsibility to help one another if they are struggling. For example, the pair team members are struggling on a area, then the other pair of team members needs to drop what they are doing to help or if one of the pair of team members one is struggling, then the other half of the pair needs to assist them. If this project is going to succeed and finish on time, then ensuring every member of the team is on board. Also, guide one another with the course submission's making sure everyone completes the course and succeeds. Finally, we all have the responsibility to communicate with one another, to the team as a whole effectively, and to Jacquelyn Donaldson, so there are no ambiguity to the development process throughout these two semesters of the course.